Named Entity Recognition as Structured Prediction

### 2012-11-11 doc/report/paper.tex
Minor changes.

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{textcomp}
\usepackage{todonotes}
\usepackage{placeins}

@@

\ex. $\text{S} \rightarrow \text{NP}\  \text{VP} $ \footnote{ A sentence (S) breaks down into a noun phrase (NP) and a verb phrase (VP)} \\
$ \text{VP} \rightarrow \text{V}\  (\text{NP})$ \footnote{ A verb phrase (VP) consists of a verb followed by an optional NP}

Thus, sentences are often represented as syntactic trees that model the dependencies among the types.
The overall type for a Named Entity is usually a noun phrase (NP), which can be both simple and complex, meaning it can consist of a only a noun phrase or 
also additional other syntactic types, such as prepositional phrases (PP), that consist of a preposition and a noun phrase. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% - can be left out if not enough space/too detailed
It is therefore a recursive definition and in theory, noun phrases can grow infinitely big, as shown by the recursive rules in example~\ref{recRules}.  %

\ex. $ \text{NP} \rightarrow \text{NP} \  \text{PP}$ \\ \label{recRules}
     $ \text{PP} \rightarrow \text{P} \  \text{NP}$ 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In order to illustrate linguistically motivated problems in NER, we consider the following problem, which is addressed in our model by a feature.

@@

For ML, supervised learning is the most common method applied in NER.
There are unsupervised methods, however they cannot currently compete with supervised applications.
For the CoNLL shared task in 2002 \cite{tksintro}, 12 systems participated in the challenge and presented a wide variety of approaches to the Named Entity task.
The most successful system used AdaBoost applied to fixed-depth decision trees. Special attention was given to a variety of input features and the features were also
partly adapted for each language with an F-score of 81.39 on the Spanish test set and 77.05 on Dutch.
The second best system \cite{Florian:2002:NER:1118853.1118863} employed three stacked
learners (transformation-based learning for obtaining base-level non-typed Named Entites, sparse network of winnows (Snow) for improving the quality of these entities and the forward-backward algorithm for finding the categories for the Named Entites), where the combination of these three algorithms substantially outperformed any subset of them, with an F-score of 79.05 on the Spanish test set and 74.99 on Dutch.
Among the most prominent algorithms in NER are maximum entropy models, whose benefit in regard to this task became most apparent in CoNLL 2003. 
For CoNLL 2003, five of the sixteen systems used this statistical learning method and three used maximum entropy models in isolation.
Maximum entropy models appear to be a suitable choice for the NER task, since systems using this approach were ranked among the three highest results in 
English and the two highest results in German \cite{TjongKimSang:2003:ICS:1119176.1119195}.
The best system in both German and English \cite{Florian:2003:NER:1119176.1119201} used a combination of classifiers: a robust linear classifier, 
a maximum entropy classifier, a transformation-based learner, and a hidden Markov model. The models were connected through a linear interpolation of the classifiers’ % combination scheme
class probability distribution. Particular importance is also assigned to creating a rich feature space, also including a gazetteer feature. 
This system achieves a F-score of 88.76\% on the English test set and 72.41\% on the German one.
Another, more recent approach involved the use of Deep Belief Nets (DBN) for NER in Chinese \cite{Chen:2010:UDB:1870457.1870473}.
Due to the special characteristics of Chinese of lacking boundary information, character-based methods are generally given preference over word-based methods.
In their application for NER, DBN  is used to automatically discover the complicated composite effects of the characters to the NE categories from the input data. 
The paper reports DBN's strong representative power in regard to detection of more complicated and efficient features. With a precision of 91.45\%,
it achieves better performance than a SVM and a BP neural networks.

@@

\begin{table}[h!]
\small
\begin{tabular}{ l l }
\bf Feature & \bf Example \\
\hline
Token &  \textbf{``Amsterdam''}\\
Suffix& Amster\textbf{dam}\\
Prefix&  \textbf{San} Sebastian\\
Captitalized& \textbf{B}enetton\\
Number Pattern & \\
UPPERCASE &  \textbf{BENETTON}\\
POS-tag &  Benetton \textbf{NNP}   \\
Lemma &  produced $\Rightarrow$ produce \\

\end{tabular}
\caption{Node Features}
\label{table:node}
\end{table}

\paragraph*{Label Interaction Features}
These features register which label has been assigned to the previous token and takes into account the most likely sequence. 
Thus, for the sequence: ``Jack London went to New York'' the NE tag combination of \emph{PER} and \emph{PER} in example~\ref{seq1} is more likely than\emph{PER} and \emph{LOC} in \ref{seq2}.
%current token and last label for prepositions or possessive ’s

@@

In addition, there is a prepositional phrase (PP) attachment feature, that registers the existence of a this attachment, that would
result in a break of the sequence as in

\exg. Bank of Scotland . \\ 
      ORG   0    ORG   0  \\\label{seq3}

@@

In the following, we show the influence of each of the three sets of features on the resulting accuracy.
\FloatBarrier
\begin{figure*}[t!]
 \includegraphics[scale=0.5]{Plot.png}
\end{figure*}

@@

In this paper, we presented a \namedentity~Recognition system based on the concept of Structured Prediction. 
While the system does not achieve state-of-the-art performance on the CoNLL shared task, we believe that the results 
are reasonable for the following reasons. We are using a simple model, which has the advantage that the final application 
will be fast and it is easily extendable. In contrast to the best systems in the CoNLL task, we also do not use ensemble 
learning methods and we use the same set of features for all languages, which enables simple extension of the system to additional languages.

>>>>

\documentclass[11pt]{article}
\usepackage{acl2011}
\usepackage[utf8]{inputenc}
\usepackage{linguex}
\usepackage{latexsym}  
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{verbatim}
\usepackage{array}
\usepackage{subfigure}
\usepackage{hyperref}
\usepackage{amsmath}
\usepackage{qtree}
\usepackage{textcomp}
\usepackage{todonotes}

@@

\ex. $\text{S} \rightarrow \text{NP}\  \text{VP} $ \footnote{ A sentence S breaks down into a noun phrase NP and a verb phrase VP} \\
$ \text{VP} \rightarrow \text{V}\  (\text{NP})$ \footnote{ A verb phrase VP consists of a verb followed by an optional NP}

Thus, sentences are often represented as syntactic trees that model the dependencies among the types.
The overall type for a Named Entity is usually a noun phrase (NP), which can be both simple and complex, meaning it can consist of a only a noun phrase or 
also additional other syntactic types, such as prepositional phrases (PP), that consist of a preposition and a noun phrase. 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% - can be left out if not enough space/too detailed
It is therefore a recursive definition and in theory, noun phrases can grow infinitely big, as shown by the following recursive rules:  %

\ex. $ \text{NP} \rightarrow \text{NP} \  \text{PP}$ \\
     $ \text{PP} \rightarrow \text{P} \  \text{NP}$ 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

To illustrate linguistically motivated problems in NER, we consider the following problem, which is addressed in our model by a feature.

@@

For ML, supervised learning is the most common method applied in NER.
There are unsupervised methods, however they cannot currently compete with supervised applications.
For the CoNLL shared task in 2002 \cite{tksintro}, 12 systems participated in the challenge and presented a wide variety of approaches to the Named Entity task.
The most successful system used AdaBoost applied to fixed-depth decision trees. Special attention was given to a variety of input features and the features were also
partly adapted for each language with an F-score of 81.39 on the Spanish test set and 77.05 on Dutch.
The second best system \cite{Florian:2002:NER:1118853.1118863} employed three stacked
learners (transformation-based learning for obtaining base-level non-typed Named Entites, Snow for improving the quality of these entities and the forward-backward algorithm for finding the categories for the Named Entites), where the combination of these three algorithms substantially outperformed any subset of them, with an F-score of 79.05 on the Spanish test set and 74.99 on Dutch.
Among the most prominent algorithms in NER are maximum entropy models, whose benefit in regard to this task became most apparent in CoNLL 2003. 
For CoNLL 2003, five of the sixteen systems used this statistical learning method and three used maximum entropy models in isolation.
Maximum entropy models appear to be a suitable choice for the NER task, since systems using this approach were ranked among the three highest results in 
English and the two highest results in German \cite{TjongKimSang:2003:ICS:1119176.1119195}.
The best system in both German and English \cite{Florian:2003:NER:1119176.1119201} used a combination of classifiers: a robust linear classifier, 
a maximum entropy classifier, a transformation-based learner, and a hidden Markov model. The models were connected through a linear interpolation of the classifiers’ % combination scheme
class probability distribution. Particular importance is also assigned to creating a rich feature space, also including a gazetteer feature. 
This system achieves a F-score of 88.76\% on the English test set and 72.41\% on the German one.
Another, more recent approach involved the use of Deep Belief Nets (DBN) for NER in Chinese \cite{Chen:2010:UDB:1870457.1870473}.
Due to the special characteristics of Chinese of lacking boundary information, character-based methods are generally given preference over word-based methods.
In their application for NER, DBN  is used to automatically discover the complicated composite effects of the characters to the NE categories from the input data. 
The paper reports DBN's strong representative power in regard to detection of more complicated and efficient features. With a precision of 91.45\%,
it achieves better performance than a SVM and a BP neural networks.

@@

\begin{table}[h!]
\small
\begin{tabular}{ l l }
\bf Feature & \bf Example \\
\hline
Token &  \textbf{Amsterdam}\\
Suffix& Amster\textbf{dam}\\
Prefix&  \textbf{Mc}Cartney\\
Captitalized& \textbf{B}enetton\\
UPPERCASE &  \textbf{BENETTON}\\
Number patterns & 2005\\
POS tag &  Benetton \textbf{NNP}   \\
Lemma & produced $\Rightarrow$ produce \\

\end{tabular}

\caption{\normalsize Examples of node features.}
\label{table:node}
\end{table}

\paragraph*{Label Interaction Features}
These features model the interaction between the labels of adjacent tokens and take into account the most likely sequence. 
For the sequence ``Jack London went to New York'', the label combination of \emph{PER} and \emph{PER} as in \ref{seq1} is more likely than \emph{PER} and \emph{LOC} in \ref{seq2}.
%current token and last label for prepositions or possessive ’s

@@

@@

In the following, we show the influence of each of the three sets of features on the resulting accuracy.

%INSERT MATLAB PIC HERE

@@

In this paper, we presented a \namedentity~Recognition system based on the concept of Structured Prediction. While the system does not achieve state-of-the-art performance on the CoNLL shared task, we believe that the results are reasonable for the following reasons: We are using a simple model, which has the advantage that the final application will be fast and it is easily extendable. In contrast to the best systems in the CoNLL task, we also do not use ensemble learning methods and we use the same set of features for all languages, which enables simple extension of the system to additional languages.
